Control Script for SCOPE data

### 2022-10-05 untargeted/output_control.Rmd
Moving hmdb formulae to metadata

```{r assignformulae, purl=FALSE}
M_area_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
feature_envelopes <- read.csv(paste0(output_folder, "feature_envelopes.csv"))
feature_data <- M_area_peaks %>%
  group_by(feature) %>%
  summarise(mzmed=median(mz), rtmed=median(rt), avg_area=mean(M_area))
stan_annotations <- read.csv(paste0(output_folder, "stan_annotations.csv"))
# database_formulae <- readRDS("unique_formulae.rds") %>%
#   gsub(pattern = "\\+.?", replacement = "")
database_formulae <- unique(readRDS("hmdb_formulae.rds"))

>>>>

```{r assignformulae, purl=FALSE}
M_area_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
feature_envelopes <- read.csv(paste0(output_folder, "feature_envelopes.csv"))
feature_data <- M_area_peaks %>%
  group_by(feature) %>%
  summarise(mzmed=median(mz), rtmed=median(rt), avg_area=mean(M_area))
stan_annotations <- read.csv(paste0(output_folder, "stan_annotations.csv"))
# database_formulae <- readRDS("unique_formulae.rds") %>%
#   gsub(pattern = "\\+.?", replacement = "")
database_formulae <- unique(readRDS("../metadata/raw_data/hmdb_formulae.rds"))
